Appendix 2: example of index standardization of fishery-independent survey data with sdmTMB

### 2021-12-14 doc/appendix-pcod-VAST-tweedie.Rmd
number appendices and cite them in paper
save sdmTMB indices and compare with VAST

---
title: "Annotated example of index standardization with VAST"
output:
  pdf_document:
    highlight: tango
---

@@

```{r plot-knots, echo = TRUE}
knitr::include_graphics(here("doc", "appendix-VAST-tweedie", "Data_and_knots.png"))
```

@@

>>>>

---
title: "Appendix 5: example of index standardization of fishery-independent survey data with VAST"
output:
  pdf_document:
    highlight: tango
---

@@

```{r plot-knots, echo = TRUE, out.width = "6in"}
knitr::include_graphics(here("doc", "appendix-VAST-tweedie", "Data_and_knots.png"))
```

@@

```{r compare-w-sdmTMB, out.width = "6in"}
library(dplyr)
library(ggplot2)
vast_i <- read.csv(here("doc/appendix-VAST-tweedie/Index.csv")) %>% 
  mutate(index = "VAST", year = as.numeric(Time), est = Estimate, se = Std..Error.for.Estimate) %>% select(index, year, est, se)
sdm_i <- readRDS("sdmTMB-index.rds") %>% mutate(index = "sdmTMB")%>% select(index, year, est, se, lwr,upr)
both_i <- bind_rows(sdm_i, vast_i) %>% filter(est > 0 )

ggplot(both_i, aes(year, est / 1000, group = index)) +
  geom_line(aes(year, est / 1000, colour = index)) +
    geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000, fill= index), alpha = 0.4) +
  geom_ribbon(aes(ymin = (est - (se*1.96)) / 1000, ymax = (est + (se*1.96)) / 1000, 
                  fill= index), alpha = 0.4) + 
  ggsidekick::theme_sleek() +
  ylab("Biomass (t)")
```

### 2021-12-14 doc/appendix-pcod-sdmTMB.Rmd
number appendices and cite them in paper
save sdmTMB indices and compare with VAST

---
title: "Annotated example of index standardization with sdmTMB"
output:
  pdf_document:
    highlight: tango
---

@@

```{r index, out.width="5in"}
qcs_grid$area <- 4 # all 2 x 2km
pred2 <- predict(
  fit,
  newdata = qcs_grid, return_tmb_object = TRUE,
  area = qcs_grid$area
)
ind <- get_index(pred2)
ggplot(ind, aes(year, est / 1000)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000), alpha = 0.4) +
  ylab("Biomass (t)")
```

@@

```{r index-sims, out.width="5in"}
ind <- get_index_sims(pred_sims, area = rep(4, nrow(pred_sims)), level = 0.95)
ggplot(ind, aes(year, est / 1000)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000), alpha = 0.4) +
  ylab("Biomass (t)")
```

>>>>

---
title: "Appendix 2: example of index standardization of fishery-independent survey data with sdmTMB"
output:
  pdf_document:
    highlight: tango
---

@@

```{r index, out.width="5in"}
qcs_grid$area <- 4 # all 2 x 2km
pred2 <- predict(
  fit,
  newdata = qcs_grid, return_tmb_object = TRUE,
  area = qcs_grid$area
)
ind <- get_index(pred2)
saveRDS(ind, "sdmTMB-index.rds")
ggplot(ind, aes(year, est / 1000)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000), alpha = 0.4) +
  ylab("Biomass (t)")
```

@@

```{r index-sims, out.width="5in"}
ind <- get_index_sims(pred_sims, area = rep(4, nrow(pred_sims)), level = 0.95)
saveRDS(ind, "sdmTMB-index-sim.rds")
ggplot(ind, aes(year, est / 1000)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000), alpha = 0.4) +
  ylab("Biomass (t)")
```
